Finding Quality Issues in SKOS Vocabularies

### 2012-03-26 conclusions.tex
contd. structure interpretation
updated related work and conclusions

In this paper we identified and defined quality issues of SKOS vocabularies and implemented them in the qSKOS quality assessment tool, which can find possible affected resources in a given SKOS vocabulary. We also analyzed a representative set of existing SKOS vocabularies and found real-world occurrences for all these issues.

Among the most omnipresent issues we found during analyzing the chosen set of vocabularies were missing or incomplete language information as well as orphan concepts. It also turned out that there is room for a more intense interlinking of SKOS vocabularies.

@@

We are aware that the quality issues we described in this work are purely quantitative indicators that, on their own, cannot be generalized into statements about the quality of a vocabulary. To learn more about the real-world impact of our work, we would like to conduct a qualitative study in which we confront taxonomists with our results. We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service.

>>>>

In this paper we identified possible quality issues in SKOS vocabularies and implemented them as quality checking functions in our qSKOS quality assessment tool. We analyzed a representative set of existing SKOS vocabularies and found  issues in all of them. Labeling and documentation issues were omnipresent and also structural issues, which require further investigation by the vocabulary maintainers, were found in most vocabularies. Although SKOS is designed for Linked Data, many existing vocabularies still resemble their closed-system origin, which results in a relatively low number of in- and out-links. Broken links is a major issue and calls for synchronization mechanisms in order to maintain navigability between concepts.

@@

We are aware that the quality issues we described in this work are purely quantitative indicators that, on their own, cannot be generalized into statements about the quality of a vocabulary. To learn more about the real-world impact of our work, we would like to conduct a qualitative follow-up study, in which we confront taxonomists with our results. We will also further collect community feedback, enhance the issues list, and set up a Web-based SKOS quality checking service. For larger vocabularies we will also increase the performance and efficiency of our quality checking algorithms.

### 2012-03-26 criteria.tex
fixed 4.2
updated related work and conclusions

\section{Possible Quality Issues in SKOS Vocabularies}\label{sec:criteria}

@@

\paragraph{QI 1: Omitted or Invalid Language Tags}

@@

\paragraph{QI 2: Incomplete Language Coverage}

@@

\paragraph{QI 3: Undocumented Concepts}

@@

\paragraph{QI 4: Label Conflicts}

@@

\paragraph{QI 5: Orphan Concepts}

@@

\paragraph{QI 6: Weakly Connected Components}

@@

\paragraph{QI 7: Cyclic Hierarchical Relations}

@@

\paragraph{QI 8: Valueless Associative Relations}

@@

\paragraph{QI 9: Solely Transitively Related Concepts}

@@

\paragraph{QI 10: Omitted Top Concepts}

@@

\paragraph{QI 11: Top Concept Having Broader Concepts}

@@

\subsection{Linked Data Specific Issues}

\paragraph{QI 12: Missing In-Links}

@@

\paragraph{QI 13: Missing Out-Links}

@@

\paragraph{QI 14: Broken Links}

@@

\paragraph{QI 15: Undefined SKOS Resources}

>>>>

\section{Quality Issues in SKOS Vocabularies}\label{sec:criteria}

@@

\paragraph{Omitted or Invalid Language Tags}

@@

\paragraph{Incomplete Language Coverage}

@@

\paragraph{Undocumented Concepts}

@@

\paragraph{Label Conflicts}

@@

\paragraph{Orphan Concepts}

@@

\paragraph{Weakly Connected Components}

@@

\paragraph{Cyclic Hierarchical Relations}

@@

\paragraph{Valueless Associative Relations}

@@

\paragraph{Solely Transitively Related Concepts}

@@

\paragraph{Omitted Top Concepts}

@@

\paragraph{Top Concept Having Broader Concepts}

@@

\subsection{Linked Data Specific Issues}\label{subsec:ld_issues}

\paragraph{Missing In-Links}

@@

\paragraph{Missing Out-Links}

@@

\paragraph{Broken Links}

@@

\paragraph{Undefined SKOS Resources}

### 2012-03-26 related_work.tex
updated related work and conclusions

% Data quality in general

The problem of ``vocabulary quality'' is closely related to the more general problem of ``data quality`'', which has intensively been discussed in data and information systems research (cf.~\cite{Batini2009}). Pipino et al.~\cite{Pipino2002} argue that dealing with data quality should involve both ``subjective perceptions of the individuals'' and ``objective measurements based on the data set in question''. We see our work as a contribution to the latter and believe that the kind of quality assessment we support must be combined with domain knowledge, and therefore human expertise, to make final quality judgements.

% Quality in Linked Data

Data quality research has also been conducted in the Semantic Web and Linked Data research areas. Hogan et. al~\cite{Hogan2010} identify four categories of common errors and shortcomings in RDF documents and also Heath and Bizer~\cite{Heath2011} summarize best practices for publishing data on the Web. However, the authors focus on RDF datasets in general without considering SKOS-specific properties.

@@

Ontology evaluation is task of measuring the quality of an ontology and has extensively been discussed by Vrandecic~\cite{Vrandecic2010}. Gangemi~\cite{Gangemi2006} introduced structural, functional and usability-related measures for ontology evaluation, Arpinar~\cite{Arpinar2006} define three types of conflicts that may occur in ontologies, and also Tartir et al.~\cite{Tartir2007} propose a framework for evaluation and ranking of ontologies. Although there are definitely overlaps between ontology evaluation and our research, the quality issues we identified are less tight to underlying data model and formal ontology definition language but, to a large extent, derived from manuals and guidelines taxonomist use in their daily work.

>>>>

% Data quality in general
The problem of ``vocabulary quality'' is closely related to the more general problem of ``data quality`'', which has intensively been discussed in data and information systems research (cf.~\cite{Batini2009}). Pipino et al.~\cite{Pipino2002} argue that dealing with data quality should involve both ``subjective perceptions of the individuals'' and ``objective measurements based on the data set in question''. We see our work as a contribution to the latter.

% Quality in Semantic Web and Linked Data
Data quality research has also been conducted in the Semantic Web and Linked Data research areas. Hogan et. al~\cite{Hogan2010} identify four categories of common errors and shortcomings in RDF documents and also Heath and Bizer~\cite{Heath2011} summarize best practices for publishing data on the Web. However, the authors focus on RDF datasets in general without considering SKOS-specific properties. Ontology evaluation is task of measuring the quality of an ontology and has extensively been discussed by Vrandecic~\cite{Vrandecic2010}.

@@

% Gangemi~\cite{Gangemi2006} introduced structural, functional and usability-related measures for ontology evaluation, Arpinar~\cite{Arpinar2006} define three types of conflicts that may occur in ontologies, and also Tartir et al.~\cite{Tartir2007} propose a framework for evaluation and ranking of ontologies. Although there are definitely overlaps between ontology evaluation and our research, the quality issues we identified are less tight to underlying data model and formal ontology definition language but, to a large extent, derived from manuals and guidelines taxonomist use in their daily work.
